---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pkgdoc

<!-- badges: start -->
[![R-CMD-check](https://github.com/maurolepore/pkgdoc/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/maurolepore/pkgdoc/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/maurolepore/pkgdoc/graph/badge.svg)](https://app.codecov.io/gh/maurolepore/pkgdoc)
<!-- badges: end -->

The goal of pkgdoc is to make it easy to create a data frame of the
documentation of multiple packages.

If you develop a universe, such as the tidyverse or tidymodels, pkgdoc helps you
to easily create a universe-wide reference for the pkgdown website of your
meta-package
([example](https://forestgeo.github.io/fgeo/articles/siteonly/reference.html#global-search)).

## Installation

``` r
# install.packages("pak")
pak::pak("maurolepore/pkgdoc")
```

## Example

```{r}
library(pkgdoc)
library(fgeo.x)
library(fgeo.plot)

universe <- c("fgeo.plot", "fgeo.x")

docs <- reference_package(universe, url = "https://forestgeo.github.io/")
docs
```

You can easily organize the documentation by concept (`#' @family`) and make
links clickable with `DT::datatable()` or `knitr::kable()`. For example:

* Datasets

```{r}
knitr::kable(subset(docs, concept == "datasets"))
```

* Autoplots

```{r}
knitr::kable(subset(docs, concept == "autoplots"))
```
