---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pkgdoc

<!-- badges: start -->
[![R-CMD-check](https://github.com/maurolepore/pkgdoc/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/maurolepore/pkgdoc/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of pkgdoc is to make it easy to create a data frame of the metadata
associated to the documentation of a collection of R packages.

If you maintain an R-package universe, it helps you to easily create a
universe-wide reference for the pkgdown website of your meta-package (e.g.
tidyverse, tidymodels).

## Installation

``` r
# install.packages("pak")
pak::pak("maurolepore/pkgdoc")
```

## Example

```{r}
library(pkgdoc)

library(tools)
library(datasets)
universe <- c("tools", "datasets")

docs <- reference_package(universe)
```

You may organize the documentation by package or concept (`#' @family`):

```{r}
# By package
subset(docs, package == "datasets")

subset(docs, package == "tools")

# By concept
datasets <- subset(docs, concept == "Datasets available by data()")
datasets

utilities <- subset(docs, concept == "utilities")
utilities
```

You may link to documentation online.

```{r}
url_template <- "https://www.rdocumentation.org/packages/{package}/versions/3.6.2/topics/{topic}.html"
linked <- reference_package("datasets", url_template = url_template)
linked["topic"]

knitr::kable(head(linked))
```


