---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# pkgdoc

[![Travis build status](https://travis-ci.org/maurolepore/pkgdoc.svg?branch=master)](https://travis-ci.org/maurolepore/pkgdoc)
[![Coverage status](https://coveralls.io/repos/github/maurolepore/pkgdoc/badge.svg)](https://coveralls.io/r/maurolepore/pkgdoc?branch=master)

The goal of __pkgdoc__ is to create dataframes of the documentation of installed packages. This helps you to mamipulate documentation accross multiple packages. For example, you can use __pkgdoc__ to create a reference of functions by concept accross multiple packages (similar to the Reference section of a [__pkgdown__](https://pkgdown.r-lib.org/) website but not limited to a single package).

## Installation

You can install the released version of pkgdoc from [CRAN](https://CRAN.R-project.org) with:

``` r
# install.packages("devtools")
devtools::install_github("maurolepore/pkgdoc")
```

## Example

```{r}
library(pkgdoc)
```

```{r example}
# Documentation of all installed packages
search_docs()

some_packages <- c("utils", "base")
search_docs(some_packages)
```

```{r}
reference_package(c("stats", "MASS"))

reference_concept(c("combine strings", "files", "PCA"))
```

```{r}
if (requireNamespace("fgeo", quietly = TRUE)) {

  reference_concept(
    "datasets", 
    url = "https://forestgeo.github.io/",
    packages = c("fgeo.x", "fgeo.plot")
  ) %>% 
    knitr::kable()
} 
```

