---
title: "Demo for chirunconf"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Demo for chirunconf}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

[pkgdoc](https://maurolepore.github.io/pkgdoc/) complements existing tools. You can use it to search documentation, similar to [RDocumentation](https://www.rdocumentation.org) but not limited to packages published on CRAN. Also you can use it to create a documentation index, similar to the _Reference_ section of [pkgdown](https://pkgdown.r-lib.org/) websites but is not limited to a single package.

The examples below use the packages projmgr and formulize, by [Emily Riederer](https://github.com/EmilyRiederer) and [Alex Hayes](https://github.com/alexpghayes).

```{r}
# By Emily
library(projmgr)
# By Alex
library(formulize)

# For data wrangling
library(dplyr)
```

## Example

You may use pkgdoc to centralize R packages developed during [chirunconf](https://chirunconf.github.io). You may create a single widget to search any documentation in all packages, or one widget per team.

### A package by Emily's team

```{r}
# Organization that serves the websites all all packages
# (Not really -- this is just a toy example)
chirunconf <- "https://maurolepore.github.io/"

pkgdoc::reference_package("projmgr", url = chirunconf) %>% 
  DT::datatable(
    escape = FALSE,
    rownames = NULL,
    options = list(search = list(search = "issues"))
  )
```

### A package by Alex's team

```{r}
pkgdoc::reference_package("formulize", url = chirunconf) %>% 
  DT::datatable(
    escape = FALSE,
    rownames = NULL,
    options = list(search = list(search = ""))
  )
```

You may use use pkgdoc to organize your documentation index by any concept created with the [roxygen2](https://github.com/klutometis/roxygen) tag `#' @family`. 

### Documentation about 'chirunconf'

```{r}
# 'chirunconf' is a fake concept, created for this demo
pkgdoc::reference_concept("chirunconf", url = chirunconf) %>% 
  knitr::kable()
```

[Get started with pkgdoc](https://maurolepore.github.io/pkgdoc/index.html)
