---
title: "pkgdoc"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### Basics

```{r}
library(dplyr, warn.conflicts = FALSE)
# Use pkgdoc and the packages you want to generate the reference for
library(pkgdoc)
library(tools)
library(datasets)

universe <- c("datasets", "tools")
url_template <- "https://www.rdocumentation.org/packages/{package}/versions/3.6.2/topics/{topic}.html"
linked <- reference_package(universe, url_template = url_template)
linked

select(linked, topic)
```

You may generate a clickable table is with `knitr::kable()`.

```{r}
pick <- linked |> 
  select(topic, title, concept, package) |> 
  head()

pick |> knitr::kable(col.names = NULL)
```

You may generate a searchable table with `DT::datatable()`.

```{r}
# `escape = FALSE` shows the link (defaults to showing the underlying URL)
pick |> DT::datatable(escape = FALSE)
```

### Organization and customization

In a meta-package you may organize the documentation of the entire universe in a
single place, maybe organized by package or concept (via `#'
@family`). You may create your own custom tables with `DT` or other packages.

```{r}
custom_table <- function(data, search = "") {
  DT::datatable(
    data,
    escape = FALSE,
    rownames = NULL,
    options = list(
      # fti =  f: filter, t: table, i: information
      dom = "fti", search = list(search = search)
    )
  )
  
}
```

* Datasets available by `data()`

```{r}
by_concept <- filter(pick, concept == "Datasets available by data()")

by_concept |> custom_table(search = "car")
```

* Documentation in `tools`

```{r}
by_package <- filter(pick, package == "tools")

by_package |> custom_table(search = "Utilities")
```

### Presentation

In a meta-package, you may use pkgdoc in an article, then use it to [override
the default Reference
component](https://pkgdown.r-lib.org/articles/customise.html#navbar-heading).

For an example see the pkgdown Reference of
[pkgdoc](https://maurolepore.github.io/pkgdoc/) and follow the link to its
source and see how it's configured in
[_pkgdown.yml](https://github.com/maurolepore/pkgdoc/blob/main/_pkgdown.yml).

