---
title: "Demo for chirunconf"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Demo for chirunconf}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

This document shows how to use [pkgdoc](https://maurolepore.github.io/pkgdoc/) to organize, search, and link documentation from multiple R packages -- all in one page. pkgdoc complements existing tools. It is similar to [RDocumentation](https://www.rdocumentation.org) but not limited to packages published on CRAN. It is also similar to the _Reference_ section of [pkgdown](https://pkgdown.r-lib.org/) websites but is not limited to a single package.

pkgdoc may be used to centralize R packages developed during [chirunconf](https://chirunconf.github.io). Suppose that during chirunconf [Emily Riederer](https://github.com/EmilyRiederer) and [Alex Hayes](https://github.com/alexpghayes) developed the packages projmgr and formulize. This document shows some ways you could use pkgdoc to show Emily's and Alex's work.

```{r}
library(dplyr)
library(projmgr)
library(formulize)
```

With pkgdoc + `DT::datatable()` you can create searchable widgets. For example, you can show the packages by different authors (or groups).

### A package by Emily

```{r}
# Organization that serves the websites all all packages
# (Not really -- this is just a toy example)
chirunconf <- "https://maurolepore.github.io/"

pkgdoc::reference_package("projmgr", url = chirunconf) %>% 
  DT::datatable(
    escape = FALSE,
    rownames = NULL,
    options = list(search = list(search = "issues"))
  )
```

### A package by Alex

```{r}
pkgdoc::reference_package("formulize", url = chirunconf) %>% 
  DT::datatable(
    escape = FALSE,
    rownames = NULL,
    options = list(search = list(search = ""))
  )
```

With pkgdoc + `knitr::kable()` you can create a static table with clickable links. For example, here we group features across multiple packages by concept (created with `#' @family`).

### `#' @family chirunconf`

('chirunconf' is a toy concept, created for this demo.)

```{r}
pkgdoc::reference_concept("chirunconf", url = chirunconf) %>% 
  knitr::kable()
```

[Visit pkgdoc](https://maurolepore.github.io/pkgdoc/index.html)
