---
title: "Demo of [pkgdoc](https://maurolepore.github.io/pkgdoc/) for the [Chicago R Unconference](https://chirunconf.github.io/)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Demo of pkgdoc for the Chicago R Unconference}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

This document shows how to use [pkgdoc](https://maurolepore.github.io/pkgdoc/) to organize, search, and link documentation from multiple R packages -- all in one page. pkgdoc complements existing tools. It is similar to RDocumentation (<https://www.rdocumentation.org/>) but not limited to packages published on CRAN. It is also similar to the _Reference_ section of pkgdown (<https://pkgdown.r-lib.org/>) websites but is not limited to a single package.

pkgdoc may be used to centralize R packages developed during Chicago R Unconference. Suppose that during chirunconf [Emily Riederer](https://github.com/EmilyRiederer) and [Alex Hayes](https://github.com/alexpghayes) developed the packages projmgr and formulize. This document shows some ways you could use pkgdoc to show Emily's and Alex's work.

#### Setup

```{r}
library(dplyr)

# By Emily
library(projmgr)
# By Alex
library(formulize)
```

#### A searchable widget

With pkgdoc + `DT::datatable()` you can create searchable widgets. For example, you can show the packages by different authors (or groups).

__A package by Emily__

```{r}
# Organization that serves the websites all all packages
# (Not really -- this is just a toy example)
chirunconf <- "https://maurolepore.github.io/"

pkgdoc::reference_package("projmgr", url = chirunconf) %>% 
  DT::datatable(
    escape = FALSE,
    rownames = NULL,
    options = list(search = list(search = "issues"))
  )
```

__A package by Alex__

```{r}
pkgdoc::reference_package("formulize", url = chirunconf) %>% 
  DT::datatable(
    escape = FALSE,
    rownames = NULL,
    options = list(search = list(search = ""))
  )
```

### A static index table

With pkgdoc + `knitr::kable()` you can create a static table with clickable links. Here for example we group features by concept, across multiple packages.

```{r}
pkgdoc::reference_concept("chirunconf", url = chirunconf) %>% 
  knitr::kable()
```

with the kableExtra package we can tweak the output like the 'Reference' section of a [pkgdown](https://pkgdown.r-lib.org/) website.

```{r, warning=FALSE}
nice_kable <- function(x) {
  x %>% 
    select(-package, -concept) %>% 
    unique() %>%
    knitr::kable(
      x, 
      format = "html",
      col.names = NULL,
      escape = FALSE
    ) %>%
    kableExtra::column_spec(1, bold = TRUE) %>% 
    kableExtra::column_spec(2, width = "20em")
}

pkgdoc::reference_concept("chirunconf", url = chirunconf) %>% 
  nice_kable()
```

