---
title: "Reference"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Reference}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

This reference overwrites the [default Reference of __pkgdown__](https://pkgdown.r-lib.org/reference/build_articles.html). It is a vignette stored in vignettes/siteonly. The file `_pkgdown.yml` contains this header:

```
navbar:
  type: default
  left:
  - text: "Reference"
    href: articles/siteonly/reference.html
```


You can see __pkgdoc__ in action [here]](https://forestgeo.github.io/fgeo/articles/siteonly/reference.html).

---

We are going to build all references with __pkgdoc__, manipulate data with __dplyr__, and build tables with __knitr__ and __DT__. 

```{r}
library(pkgdoc)
library(dplyr)
library(knitr)
library(DT)
```

## All functions in pkgdoc

Let's see what documentation we have to decide the best way to present it.

```{r}
docs <- reference_package("pkgdoc", url = "https://maurolepore.github.io/")
docs
```

The functions are few and we can show them all at once. But let's emphasize the main functions by pushing the helper function to the bottom. Then let's hide the column `concept`. `knitr::kable()` will transform the ugly text into links. The column `package` isn't helpful but I'll leave it to show the link.

```{r}
docs %>% 
  arrange(desc(concept)) %>% 
  select(-concept) %>% 
  knitr::kable()
```

That's cool but __pkgdown__ does it already. Next let's see a more complex example where __pkgdoc__ is really useful.

## Example: Referencing objects across multiple packages

To show how to reference objects across multiple packages we will use the __fgeo__ meta-package [__fgeo__](https://forestgeo.github.io/).

```{r}
library(fgeo)

fgeo:::fgeo_packages()

fgeo_url <- "https://forestgeo.github.io/"

```

### Searching

You can reference a large number of objects. Instead of scanning a long list your readers may prefer to search.

```{r}
# Pulling documentation of all fgeo packages
docs <- fgeo:::fgeo_packages() %>% 
  purrr::map_dfr(reference_package, url = fgeo_url) %>% 
  select(-package, -concept) %>% 
  unique()

docs %>% 
  DT::datatable(
    escape = FALSE,
    rownames = NULL,
    options = list(
      # f: filter, t: table, i: information
      dom = "fti",
      search = list(search = "topography")
    )
  )
```

### Scanning

If the list isn't too long, your reader may scan the entire list. Sometimes it is nice to know you have seen it all.

#### Grouping multiple packages

You may cherry-pick all objects from specific packages.

```{r}
reference_package(
  c("fgeo.x", "fgeo.analyze"), 
  url = fgeo_url
 ) %>% 
  arrange(concept) %>% 
  select(-package, -concept) %>% 
  knitr::kable()
```

#### Grouping concepts from multiple packages

You may cherry-pick all objects matching some concept. Create topics by adding the tag `@family` in your documentation  (see [__roxygen2__](https://cran.r-project.org/web/packages/roxygen2/vignettes/rd.html)).

```{r}
reference_concept(
  c("habitat functions", "plot functions"),
  url = fgeo_url,
  # limit the search of documentation within these packages
  packages = fgeo:::fgeo_packages(),
  ) %>% 
  arrange(concept) %>%
  select(-package, -concept) %>% 
  knitr::kable()
```
