---
title: "Reference"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Reference}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

This reference overwrites the [default Reference of __pkgdown__](https://pkgdown.r-lib.org/reference/build_articles.html). It is a vignette stored in vignettes/siteonly. The `_pkgdown.yml` file contains this header:

```
navbar:
  type: default
  left:
  - text: "Reference"
    href: articles/siteonly/reference.html
```

You can see __pkgdoc__ in action [here](https://forestgeo.github.io/fgeo/articles/siteonly/reference.html).

---

Let's build references with __pkgdoc__, manipulate data with __dplyr__, and build tables with __knitr__ and __DT__. 

```{r}
library(pkgdoc)
library(dplyr)
library(knitr)
library(DT)
```

## All functions in pkgdoc

Let's see what documentation we have to decide the best way to present it.

```{r}
docs <- reference_package("pkgdoc", url = "https://maurolepore.github.io/")
docs
```

The functions are few and we can show them all at once. But let's tweak the output:

* Let's emphasize the main functions by pushing the helper function to the bottom.
* Let's hide the `concept` column. 
* Let's build transform the ugly text in `topic` and `package` into links. 

(The column `package` isn't helpful but I'll leave it to show the link.)

```{r}
docs %>% 
  arrange(desc(concept)) %>% 
  select(-concept) %>% 
  knitr::kable()
```

Okay, but __pkgdown__ does that already. To see the value of __pkgdoc__ let's explore a more complex example.

## Example: Referencing documentation across multiple packages

To show how to reference documentation across multiple packages we will use the __fgeo__ meta-package [__fgeo__](https://forestgeo.github.io/).

```{r}
library(fgeo)

fgeo:::fgeo_packages()

fgeo_url <- "https://forestgeo.github.io/"
```

### Searching

You can reference a large number of documentation. Instead of scanning a long list your readers may prefer to search.

```{r}
# Pulling documentation of all fgeo packages
docs <- fgeo:::fgeo_packages() %>% 
  purrr::map_dfr(reference_package, url = fgeo_url) %>% 
  select(-package, -concept) %>% 
  unique()

docs %>% 
  DT::datatable(
    escape = FALSE,
    rownames = NULL,
    options = list(
      # f: filter, t: table, i: information
      dom = "fti",
      search = list(search = "topography")
    )
  )
```

### Scanning

If the list isn't too long, your reader may scan the entire list. Sometimes it is nice to know you have seen it all.

#### Grouping multiple packages

You may cherry-pick all documentation from specific packages.

```{r}
reference_package(
  c("fgeo.x", "fgeo.analyze"), 
  url = fgeo_url
 ) %>% 
  arrange(concept) %>% 
  select(-package, -concept) %>% 
  knitr::kable()
```

#### Grouping concepts from multiple packages

You may cherry-pick all documentation matching some concept. Create topics by adding the tag `@family` in your documentation  (see [__roxygen2__](https://cran.r-project.org/web/packages/roxygen2/vignettes/rd.html)).

```{r}
reference_concept(
  c("habitat functions", "plot functions"),
  url = fgeo_url,
  # limit the search of documentation within these packages
  packages = fgeo:::fgeo_packages(),
  ) %>% 
  arrange(concept) %>%
  select(-package, -concept) %>% 
  knitr::kable()
```
