---
title: "tidyverse reference"
subtitle: "Created by the [pkgdoc package](https://maurolepore.github.io/pkgdoc/)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tidyverse reference}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

WARNING: This reference may be out of date. It aims to demonstrate __pkgdoc__ -- not to provide a search tool for the tidyverse.

```{r}
library(pkgdoc)
library(tidyverse)
library(glue)
library(DT)

(docs <- reference_package(tidyverse:::core) %>% arrange(package))
```

`reference_package()` and `reference_concept()` include the argument `url` but it only works if all packages are under the GitHub organization and the url is formatted as `https://{organization}.github.io/{package}/`. But we can create arbitrary links easily with `glue::glue()`.

```{r}
linked <- mutate(
  docs,
  topic   = glue("<a href=https://{package}.tidyverse.org/reference/{topic}>?</a>"),
  package = glue("<a href=https://{package}.tidyverse.org/index.html>{package}</a>")
)
```

We are almost ready. Let's arrange the documentation by package and use `DT::datatable()` to create clickable links.

```{r}
linked %>% 
  arrange(.data$package) %>% 
  datatable(
    escape = FALSE,
    rownames = NULL,
    options = list(
      # f: filter, t: table, i: information
      dom = "fti",
      search = list(search = "filter")
    )
  )
```




